The SMT Competition 2015--2018

### 2019-04-15 2018/report/SMT-COMP.tex
small fix in division scoring

\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016-2018).}
The \emph{(weighted) score} of a solver in a division of the \maintrack and
\ucoretrack with $M$ benchmarks is then defined as the weighted sum of all raw
scores $$\sum_{b\in M} \alpha'_b \cdot \langle e_b \cdot N_b, n_b \cdot N_b,
w_b, c_b\rangle$$ where the sum is over all benchmarks in the division to
assess parallel performance, and the weighted sum of all sequential scores to
assess sequential performance.

>>>>

\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016-2018).}
The \emph{(weighted) score} of a solver in a division of the \maintrack and
\ucoretrack with $M$ benchmarks is then defined as the weighted sum of all raw
scores $$\sum_{b\in M} \alpha'_b \cdot \langle e_b \cdot N, n_b \cdot N,
w_b, c_b\rangle$$ where the sum is over all benchmarks in the division to
assess parallel performance, and the weighted sum of all sequential scores to
assess sequential performance.
